---
title: "Lab10"
author: "Ali Haydar Ozgun"
date: "11/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The re-analysis should focus only on Experiment 3. There are three main goals

1. Reproduce as much of the analysis as possible using only paired-sample t-tests. Note, the authors reported a 2x2 repeated measures ANOVA, but consider how the same questions could be answered by t-tests

2. Reproduce a graph of the means, like shown in the paper

3. Present a power-curve analysis for the design. (2 points)


```{r}

library(dplyr)
library(ggplot2)
library(tidyr)

```


```{r}
all_data <- read.csv('open_data/stroop_stand.csv')
  
# Computing the stroop effect for standing condition;

(stand_stroop <- t.test(all_data$incongruent_stand,
                       all_data$congruent_stand,
                       paired = TRUE)) # We do the paired sample t-test to comparing to datain                                       # congurent stand column. 

# Computing the stroop efffect for sit condition;

(sit_stroop <- t.test(all_data$incongruent_sit,
                     all_data$congruent_sit,
                     paired = TRUE))


  
```



```{r}

stand_stroop_scores <- all_data$incongruent_stand - all_data$congruent_stand

sit_stroop_scores <- all_data$incongruent_sit - all_data$congruent_sit


stroop_differences <- sit_stroop_scores - stand_stroop_scores

(paired_results <- t.test(stand_stroop_scores,
                         sit_stroop_scores,
                         paired = TRUE))

(interaction_result <- t.test(stroop_differences)) # with this code we do one sampled t-test


```



```{r}

# converting the data from wide format to long

stroop_df <- all_data %>% 
  pivot_longer(cols = 1:4,
               names_to = c('Congruency', 'Posture'),
               names_sep = '_',
               values_to = 'RTs')


# Calculating the means;

overall_means <- stroop_df %>% 
  group_by(Posture, Congruency) %>% 
  summarise(meanRT = mean(RTs),
            SEMRT = (sd(RTs) / sqrt(length(RTs))))



# Ploting the data;

ggplot(overall_means, aes(x = Posture,
                          y = meanRT,
                          group = Congruency,
                          fill = Congruency)) +
  geom_bar(stat = 'identity', position = 'dodge') +
  theme_classic(base_size = 12) +
  ylab('Mean Reaction Time (ms)') +
  geom_errorbar(aes(ymin = meanRT - SEMRT,
                    ymax = meanRT + SEMRT),
                position = position_dodge(width = 0.9),
                width = .2,
                color = 'black') +
  coord_cartesian(ylim = c(500, 1000))


```



```{r}

# Power-curve Analysis

effect_sizes <- seq(0, 1.5, .1)

prop_significant <- c()

for(i in 1 : length(effect_sizes)){
  sim_ps <- replicate(1000, t.test(replicate(50, rnorm(1, effect_sizes[i], 1)),
                                   mu = 0)$p.value)
  
  prop_significant[i] <- length(sim_ps[sim_ps < .05]) / 1000
}

plot_df <- data.frame(effect_sizes,
                      prop_significant)


ggplot(plot_df, aes(x = effect_sizes, y = prop_significant)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = seq(0, 1.5, .1)) +
  scale_y_continuous(breaks = seq(0, 1, .1)) +
  ylab('Proportion Significant')


```












