---
title: "Lab5"
author: "Ali Haydar Ozgun"
date: "10/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Problem 1; Trust but verify. We trust that the rnorm() will generate random deviates in accordance with the definition of the normal distribution. For example, we learned in this lab, that a normal distribution with mean = 0, and sd =1 , should only produce values larger than 2.5 with a specific small probability, that is P(x>2.5) = 0.006209665. Verify this is approximately the case by randomly sampling 1 million numbers from this distribution, and calculate what proportion of numbers are larger than 2.5.


```{r}

library(ggplot2) 
library(dplyr)  

# We will use the pnorm function to getting P(x>2.5) = 0.006209665

pnorm(2.5, mean = 0, sd = 1, lower.tail = FALSE)

# For the fallowing step we need to sample 1000000 from the previous distribution

random_sampling <- rnorm(1000000, mean = 0, sd = 1)

# As the next step we need to show the verification 

selected_sample <- random_sampling[random_sampling > 2.5]

length(selected_sample)

length(selected_sample) / 1000000 # this gave us 0.006218, and that verifies how the rnorm functions produces well sugessted numbers


```

Helping Rate : 90

 

Problem 2; If performance on a standardized test was known to follow a normal distribution with mean 100 and standard deviation 10, and 10,000 people took the test, how many people would be expected to achieve a score higher than 3 standard deviations from the mean?


```{r}

# In the question when said a score higher than 3 standard deviation from the mean, we can say that the vector of quantiles is 130. 

pnorm(130, mean = 100, sd = 10, lower.tail = FALSE, log.p = FALSE) #0.001349898 probability

# To find how many people would get a score higher than 3 standard deviations from the mean, we need to multiply the probability by the total number of the person who took the exam. 

10000 * pnorm(130, mean = 100, sd = 10, lower.tail = FALSE, log.p = FALSE) #13.49898 person scored higher than 3 standard deviation from the mean. 


### Other possible solution is;

people_scores <- rnorm(10000, mean = 100, sd = 10)

people_scores[people_scores > 130]

10000 * (length(people_scores[people_scores > 130] ) / 10000)

```

Helping Rate : 80





Problem 3; You randomly sample 25 numbers from a normal distribution with mean = 10 and standard deviation = 20. You obtain a sample mean of 12. You want to know the probability that you could have received a sample mean of 12 or larger. Create a sampling distribution of the mean for this scenario with at least 10,000 sample means. Then, calculate the proportion of sample means that are 12 or larger.

```{r}

rnorm(25, mean = 10, sd = 20) # randomly sampling 

mean(rnorm(25, mean = 10, sd = 20)) # checking the mean

## Creating a sampling distribution of the mean for this scenario with at least 10,000 sample means; 


sample_distribution <- replicate(10000, mean(rnorm(25, mean = 10, sd = 20)))


hist(sample_distribution) # checking the distribution on the histogram


# For calculating the proportion of sample means that that are 12 or larger; 

length(sample_distribution[sample_distribution >= 12]) / 10000 # we used '' >='' because in the question was asked that are 12 or larger



```


Helping Rate : 90


Problem 4; You randomly sample 100 numbers from a normal distribution with mean = 10 and standard deviation = 20. You obtain a sample mean of 12. You want to know the probability that you could have received a sample mean of 12 or larger. Create a sampling distribution of the mean for this scenario with at least 10,000 sample means. Then, calculate the proportion of sample means that are 12 or larger. Is the proportion different from question 3, why? 



```{r}

sample_numbers <- replicate(10000, mean(rnorm(100, mean = 10, sd = 20)))

hist(sample_numbers)

length(sample_numbers[sample_numbers >= 12]) / 10000 

# When we compare the question 3 and question 4, we see that in the question 4 the probability is smaller than the question 3. So, the proportion is lower than the question 3. Because the distribution would not be normal, would be more leptokurtic. For the statistical hypothesis testing, when the sample size increased, our z-score would increase too, so the null hypothesis would reject.

```

Helping Rate : 80




Problem 5; You randomly sample 25 numbers from a normal distribution with mean = 10 and standard deviation = 20. You obtain a sample standard deviation of 15. You want to know the probability that you could have received a sample standard deviation of 15 or less.Create a sampling distribution of standard deviations for this scenario with at least 10,000 sample standard deviations. Then, calculate the proportion of sample standard deviations that are 15 or less.


```{r}
random_scores <- replicate(10000, sd(rnorm(25, mean = 10, sd = 20)))

hist(random_scores)

length(random_scores[random_scores <= 15]) / 10000 
```


Helping Rate : 90



