---
title: "Lab8"
author: "Ali Haydar Ozgun"
date: "10/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Problem 1; Write a function to convert a vector of raw-scores into z-scores. The function should have inputs for the vector, the mean and sd of the normal distribution, and should return a vector of zscores.Also, demonstrate that the function works correctly.  How you make the demonstration is up to you.

- Advanced: Have an option so that the function will convert the raw scores to zscores in one of two ways:
- using user provided mean and standard deviation
- using the calculated mean and standard deviation from the raw scores

```{r}


# Computing mean and sd from scores;

example_numbers <- c(1, 2, 3, 4, 5)
mean(example_numbers)
sd(example_numbers)


(example_numbers - mean(example_numbers)) / sd(example_numbers)

# Computing z-score from known mu and sd;

example_numbers <- c(1, 2, 3, 4, 5)

mu <- 3
sigma <- 1

(example_numbers - mu) / sigma

# Putting everything in a function

raw_to_zscore <- function(raw_scores, mu, sigma){
  z_score <- (raw_scores - mu) / sigma
  return(z_score)
  
}


raw_to_zscore(raw_scores = c(1, 2, 3, 4, 5),
              mu = 3,
              sigma = 1)


```

Helping Rate : 40

 

Problem 2; Base R does not have a function for a z-test. Write a function to accomplish a one-sample z-test. Remember, a one-sample z test is used to compare the probability of obtaining the sample mean (or larger or smaller) if it came from a known normal distribution.

- Use your z-test function to conduct a test of the following. A sample of 25 scores is taken. The mean of the sample is 50. The sample is assumed to have been taken from a normal distribution with mean 40 and standard deviation 7. Report a one-tailed z-test, examining the probability of obtaining a sample of greater than 50 in this situation. Report the results, and give a brief sentence explaining the result and the inference you make


```{r}

z_test <- function(sample_mean, sample_size, mu, sigma){
  sample_distribution_mean <- mu
  sample_distribution_sd <- sigma / sqrt(sample_size)
  
  p_value <- pnorm(sample_mean, sample_distribution_mean, sample_distribution_sd,
                   lower.tail = FALSE)
  return(p_value)
  
}

z_test(sample_mean = 50,
       sample_size = 25,
       mu = 40,
       sigma = 7)

### 4.570531e-13 = 0.0000000000004570531 that means we got really small p-value for 25 sample size, and 50 sample mean distribution. 

```

Helping Rate : 40









