---
title: "Lab9"
author: "Ali Haydar Ozgun"
date: "11/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Problem ; 

- The following paper links to open data, and describes a design where two chi-square tests are performed for Experiment 1 (A copy of this paper will be made available).

Silver, A. M., Stahl, A. E., Loiotile, R., Smith-Flores, A. S., & Feigenson, L. (2020). When Not Choosing Leads to Not Liking: Choice-Induced Preference in Infancy. Psychological Science, 0956797620954491.

Obtain the data from the online repository, show your code for loading it into R, then conduct the same tests reported in Experiment 1 that the authors conducted. These include one binomial test, and two chi-square tests. Briefly report your re-analysis, and discuss whether you obtained the same values as the authors did (6 points).




```{r}
#loading the data;

library(readxl)

When_not_choosing_leads_to_not_liking_Data <- read_excel("open_data/When not choosing leads to not liking_Data.xlsx")


dim(When_not_choosing_leads_to_not_liking_Data)


```

#Reproducing the binomial test

```{r}

library(dplyr)


experiment1 <- When_not_choosing_leads_to_not_liking_Data %>% 
  filter(ExperimentNumber == 1)

number_chose_C <- sum(experiment1$'Infant Chose C')

number_chose_C

binom.test(x = number_chose_C,
      n = dim(experiment1)[1],
      p = .5,
      alternative = 'two.sided')

# The binomial test in the original article found that 76.2% chose the new block significantly different from chance. And here, we found the probability of success 0. 7619048, which is the same as their findings.  

# Also our p-value (0.0266) and 95 percent confidence interval(0.5283402, 0.9178241) are similar to the original article.

```

#Reproducing the chi-square test for gender;

```{r}

library(tidyr)

gender_choice_table <- experiment1 %>% 
  group_by(Gender, `Infant Chose C`) %>% 
  summarize(counts = n()) %>% 
  pivot_wider(names_from = c(Gender),
              values_from = counts)

gender_choice_table <- gender_choice_table[,2:3]

(gender_Xsq <- chisq.test(gender_choice_table))

uncorrected_Xsq <- sum((gender_Xsq$observed-gender_Xsq$expected)^2 / gender_Xsq$expected)

uncorrected_Xsq

gender_Xsq_unc <- pchisq(uncorrected_Xsq, 1, lower.tail = FALSE)

gender_Xsq_unc


# Findings of chi-square test for gender are showed the similarity on chi-square = 0.15 (in our findings 0.1527273), and p = .696 (in our findings 0.6959426)

```



