---
title: "Reproducible Report"
author: "Ali Haydar Ozgun"
date: "12/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction


This report re-produces the analysis of Experiment 4 reported in Mehr, Song, Spelke (2016). The citation for the article is:

Mehr, S. A., Song, L. A., & Spelke, E. S. (2016). For 5-month-old infants, melodies are social. Psychological Science, 27(4), 486-501.

The data were downloaded from [https://osf.io/y3kzd/files/](https://osf.io/y3kzd/files/)

Mehr et al. (2016) had 5- month old infants participants and their parents 



## Re-analysis

```{r}

# Loading the libraries and data

library(dplyr)
library(ggplot2)
library(tidyr)


all_data <- read.csv('LUL_pss.csv')

experiment_four <-  all_data %>% filter(exp4 == 1)

# Toy playing familiar song;

familiar_song <- experiment_four$famtot_6

mean(familiar_song)

sd(familiar_song)


# Toy playing unfamiliar song;

un_familiar <- experiment_four$unfamtot_6

mean(un_familiar)

sd(un_familiar)

# Paired sample t-test;

t.test(familiar_song, un_familiar, paired = TRUE, var.equal = TRUE)


# difference_scores <- experiment_four$mbabylike - experiment_four$mtotrecord

difference_scores <- experiment_four$mtotrecord - experiment_four$mbabylike

# difference_scores <- experiment_four$mtotsing - experiment_four$delay


t.test(difference_scores, mu = .1)




```
```{r}

#data.frame(familiar_song, un_familiar)


```


### Table of Means


### Reproducing the Plot


### T-test