---
title: "Reproducible Report"
author: "Ali Haydar Ozgun"
date: "12/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction


This report re-produces the analysis of Experiment 4 reported in Mehr, Song, Spelke (2016). The citation for the article is:

Mehr, S. A., Song, L. A., & Spelke, E. S. (2016). For 5-month-old infants, melodies are social. Psychological Science, 27(4), 486-501.

The data were downloaded from [https://osf.io/y3kzd/files/](https://osf.io/y3kzd/files/)

Mehr et al. (2016) had 5- month old infants participants and their parents 



## Re-analysis

```{r}

# Loading the libraries and data

library(dplyr)
library(ggplot2)
library(tidyr)


all_data <- read.csv('LUL_pss.csv')


experiment_four <- all_data %>% filter(exp4 == 1)



```


### Table of Means
```{r}

mean_table <- data.frame(
  ToyPlaying = rep(c("Familiar Song", "Unfamiliar Song")),
  LookingTime = c(experiment_four$famtot_6, experiment_four$unfamtot_6))

group_by(mean_table, ToyPlaying) %>% 
  summarise(
    count = n(),
    mean = mean(LookingTime),
    sd = sd(LookingTime))

```


### Reproducing the Plot


```{r}
library(ggplot2)


mean_table <- data.frame(
  ToyPlaying = rep(c("Familiar Song", "Unfamiliar Song")),
  LookingTime = c(experiment_four$famtot_6, experiment_four$unfamtot_6))

group_by(mean_table, ToyPlaying) %>% 
  summarise(
    count = n(),
    mean = mean(LookingTime),
    sd = sd(LookingTime))

ggplot(mean_table, aes(x = ToyPlaying, y = LookingTime, color = ToyPlaying)) +
  geom_boxplot()


```



### Conducting t-test;

```{r}

t.test(experiment_four$famtot_6, experiment_four$unfamtot_6, paired = TRUE)


```

### Power analysis

```{r}

library(pwr)
effect_sizes <- seq(.1,2,.1)
power_analysis <- sapply(effect_sizes,
          FUN = function(x) {
            pwr.t.test(n=22,
            d=x,
            sig.level=.05,
            type="paired",
            alternative="two.sided")$power})
plot_df <- data.frame(effect_sizes,power_analysis)

library(ggplot2)
ggplot(plot_df, aes(x=effect_sizes,
                    y=power_analysis))+
  geom_point()+
  geom_line()

```



### Results

Mean Looking times for difference in Toy Playing for Familiar Song and Unfamiliar Song were submitted to paired sample t-test.

The re-analysis for the differences between Familiar and Unfamiliar songs showed, Md = 24.45, 95% CI [3.04, 45.87], t(21) = 2.38, p = .027.


### Discussion

The re-analysis successfully reproduced the analysis reported by Mehr et al. (2016). Results of the analysis showed in the `SemesterProject.Rmd` that uses `papaja` to write an APA paper.









