---
title             : "Reanalysis of 'For 5-Month-Old Infants, Melodies Are Social' Study "
shorttitle        : " Semester Long Project PSYC 7765/66"

author: 
  - name          : "Ali Haydar Ozgun"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "2900 Bedford Avenue"
    email         : "alihaydar.ozgun96@bcmail.cuny.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing


affiliation:
  - id            : "1"
    institution   : "CUNY - Brooklyn College"

authornote: |
  Ali Haydar Ozgun Brooklyn College Psychology Department, Master of Art Experimental Psychology Program First Semester Student.

  

abstract: |
  This report re-produces the analysis of Experiment 4 reported in @mehr20165. The citation for the article is:
  
  @mehr20165. For 5-month-old infants, melodies are social. Psychological Science, 27(4), 486-501.
  
  The data were downloaded from [https://osf.io/y3kzd/files/](https://osf.io/y3kzd/files/).
  
   @mehr20165 had 5- month old infants participants and their parents
  
  
  
  <!-- https://tinyurl.com/ybremelq -->

  

bibliography      : ["r-references.bib","myReferences.bib"]

floatsintext      : no
figurelist        : yes
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

This report re-produces the analysis of Experiment 4 reported in @mehr20165. The citation for the article is:
  
@mehr20165. For 5-month-old infants, melodies are social. Psychological Science, 27(4), 486-501.
  
The data were downloaded from [https://osf.io/y3kzd/files/](https://osf.io/y3kzd/files/).
  
@mehr20165 had 5- month old infants participants and their parents
  

# Methods


## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results


```{r}

# Plotting


```



# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
